---
title: "Love vs extraterrestials"
author: "Jose Trejo"
date: "Spring 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
help("m111surveyfa13")
mydata<-m111surveyfa13 <- na.omit(m111surveyfa13)
```

# A question of Belief

Your data is in the dataframe called "mydata" examine it in the environment tab  
do a variable analysis on the 3 Questions and then upload the appropriate Rmd template for this job.   
Also create an empty github repository called "Belief" and make it the remote repository for  
this assignment.  For each question supply graphical evidence, numerical summaries, an inferential test, and a conclusion.  When finished push your rmd file, your project file, and your knitted html file to your github repo.  Finally turn in to Canvas the link to your github repo.




# Your First Question  

### Do people who believe in Love at First sight also tend to believe in Life on other planets?

 Do people who believe in love at first sight also tend to believe in extra terestrials. 
 
$H_o$There is no relation between people who believe in love at first sight and believeing in extra terestrials
$h_a$ There is a relation between those people who believe in love at first sight and believing in extra terestrials.
graphic display  

```{r}
barchartGC(~love_first + extra_life,data=mydata, xlab='love @ first sight')
```

People who believe in love at first sight also tend to believe believe in extra terestrials.

Numerical Summary
```{r}
table1 <- xtabs(~love_first + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```

It appears to be that people who believe in love at first sight is about the same as the ones who believe in extra terestrials.    

Inference

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


# Your second Question  

### Is there a difference between boys and girls with respect to belief in life on other planets?
  
```{r}
barchartGC(~sex + extra_life,data=mydata)
```

 
# Your last Question   

### Is there a difference between boys and girls with respect to belief in love at First sight?

```{r}
barchartGC(~sex + love_first,data=mydata)
```

